### 2014-09-19 fundamentals/impl.tex
rough draft of RIF section

\subsection{Agent Interchangability}
% interchangeability due to exchange behavior api

@@

\Cyclus provides a novel representation of entities in the nuclear fuel cycle,
including facilities, institutions managing those facilities, and regions. While
some simulators (TODO cite DESAE) have provided a notion of static regional
effects, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles.

Cyclus has three core agent classes that be subclassed to create a simulation
archetype: Region, Institution, and Facility. At present, Regions, Institutions,
and Facilities (RIF) conceptually form a nested structure in a Cyclus simulation,
i.e., Facilities exist in (i.e., are managed by) Institutions and Institutions
exist in Regions.

Importantly, the RIF separation allows for preferential trading. For example,
Facilities in the same Institution can preferentially trade with each
other. Similarly, Regions can be given a location proxy, and the trade between
Facilities can be informed by their regional proximity.

>>>>

\subsection{Agent Interchangability}\label{sec:interchangeability}
% interchangeability due to exchange behavior api

@@

\Cyclus provides a novel representation of entities in the nuclear fuel cycle,
including facilities, institutions managing those facilities, and regions. While
some simulators (\TODO{cite DESAE}) have provided a notion of static regional
effects, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles.

The basic interaction models for each entity is implemented by a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by subclassing the appropriate class.

\Cyclus implements a Region-Institution-Facility (RIF) relationship through the
parent-child hierarchy described in \S \ref{sec:interchangeability}, where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, RIF hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

Two primary consequences arise from this structure. First, institutions are
responsible for building and decommissioning facilities. Accordingly, advanced
logic regarding building and decommissioning can be obtained by subclassing the
\Class{Institution} interface. Second, the \Class{Facility} class implmenets the
\Class{Trader} interface, and thus institutions and regions, respectively, can
adjust the resource flow preferences of their managed facilities. Importantly,
this novel capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).
